CONEM2024-0025\\ ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-02-05 accepted/CONEM2024/FCPCOM/CONEM2024.tex
my beautiful equation :)

Then, the equation can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:

\begin{equation}
	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum{w_{\beta_b}*w_{p\beta_b}}
\end{equation}

>>>>

Equation (\ref{eq:weight}) can be used for calculation of multicriteria classification weights of each product, $\rho_{p}$:

\begin{equation}
	\label{eq:weight}
	\rho_{p} = (wb + wlt) * \frac{b_p}{lt_p} + \sum_{q=1}^{\textrm{NQ}}{w_{\sigma_q}*\frac{b_{e_{p\sigma_q}}}{lt_{e_{p\sigma_q}}}} + \sum_{b=1}^{\textrm{NB}}{w_{\beta_b}*w_{p\beta_b}}, \quad p= 1,...,\textrm{NP}
\end{equation}
